Patterns of floral and chromosome evolution in Onagraceae: a fossil-calibrated supermatrix analysis

### 2014-05-07 manuscript.tex
added mesquite figures

\paragraph{Floral evolution}
The maximum likelihood estimate of petal color for the 
last common ancestor of Onagraceae was pink 
with a proportional likelihood ($PL$) of $0.61$.
White was the second most likely estimate ($PL=0.11$).
The maximum likelihood estimate of petal number for the
last common ancestor of Onagraceae was 4 ($PL=1.0$), with 15
independent transitions to 0, 2, 5, or 6 petals (Figure XXXX).
Petal color and petal number were found to significantly covary over the 
phylogeny ($D=0.263, p=0.00$). Multiple signficant correlations
($d_{ij}$) were found between individual states of each character
and are summarized in Table \ref{correlations}.

@@

>>>>

\paragraph{Floral evolution}
The maximum likelihood estimate of petal color for the 
last common ancestor of Onagraceae was pink 
with a proportional likelihood ($PL$) of $0.61$ (Figure \ref{petal_color}).
White was the second most likely estimate ($PL=0.11$).
The maximum likelihood estimate of petal number for the
last common ancestor of Onagraceae was 4 ($PL=1.0$), with 15
independent transitions to 0, 2, 5, or 6 petals (Figure \ref{petal_number}).
Petal color and petal number were found to significantly covary over the 
phylogeny ($D=0.263, p=0.00$). Multiple signficant correlations
($d_{ij}$) were found between individual states of each character
and are summarized in Table \ref{correlations}.

@@

\begin{figure*}[p]
    \vspace*{-2cm}
    \makebox[\linewidth]{
        \includegraphics[width=1.6\linewidth, trim=0 0 0 0, clip=true]{petal_color}
    }
    \caption{
      Maximum likelihood ancestral state reconstruction of petal color.
      Black represents absence of petals. Vertical time scale is in millions of years before present.
    }
    \label{petal_color}
\end{figure*}

\begin{figure*}[p]
    \vspace*{-2cm}
    \makebox[\linewidth]{
        \includegraphics[width=1.6\linewidth, trim=0 0 0 0, clip=true]{petal_number}
    }
    \caption{
    Maximum likelihood ancestral state reconstructions of petal number. 
    White = 0, Blue = 2, Green = 4, Yellow = 5, Red = 6. Vertical time scale is in millions of years before present.
    }
    \label{petal_number}
\end{figure*}
